Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-08 paper.tex
add publish (2-col ans trans style) target and tweak layout

\documentclass{ntmanuscript}

@@

\usepackage{graphicx}
\usepackage[printwatermark]{xwatermark}
\usepackage{xcolor}

@@

There are various low level phenomena that have potential to affect the larger
outcome of simulations with respect to facility modeling decisions.  One
potential difference caused by fleet-based modeling involves fuel sharing.
Power production by a group of individual reactors for a fixed amount of fuel
shortage may vary depending on how the existing fuel is distributed.  This is
illustrated in Figure \ref{fig:fuel-sharing}.  Being short 3 batches might
mean that one reactor has no batches and isn't operating or that 3 reactors
are missing a single batch.  This will be referred to as the \emph{fuel
sharing effect}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.70\textwidth]{exp2/fuel-sharing.pdf}
    \caption[The fuel sharing effect]{
        A simple diagram showing effects of constrained fuel supply
        distribution choices. In both cases A and B, reactor 1 needs 3 new
        fuel batches to operate and reactors 2 and 3 each need 1 fresh batch.
        In case A, the two batches are given to reactors 2 and 3, resulting in
        reactor 1 remaining offline. In case B, the available fuel batches are
        given to reactor 1 resulting in all three reactors being offline.
    }
    \label{fig:fuel-sharing}
\end{figure}

Another difference between the fleet and individual modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short a half batch of fuel it will produce $\frac{5}{6}\cdot C$ of
power for that time step where $C$ is the power capacity of a single reactor
of the fleet (e.g. 1000 MWe).  If an individually modeled reactor is short a
half batch of fuel, then it will produce no power that time step.  Time step
duration can also have this effect.  For both fleet and individual reactor
modeling, power goes offline in for full time steps.  For example, if a
3-batch fleet based reactor is short $\frac{1}{2}$ batch of fuel with a 3
month time step, then it will produce $\frac{5}{6} \cdot 3 \text{mo} \cdot C $ of
energy.  In contrast, a monthly time step might allow the same reactor to
produce $[\frac{5}{6} \cdot 1 \text{mo} + 2 \text{mo}] \cdot C $ of energy if there was
actually a fuel shortage for only 1 month.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/sync-cycle.eps}
    \caption[The cycle staggering effect]{
        In this scenario, reactors are deployed annualy with a refueling cycle
        length (including outage) of 18 months.  So all reactors deployed
        every 3rd year refuel together.  All initial 100 LWRs start out with
        their cycles synced as well.  While it may look like separate curves,
        this plot shows only a single time series.
    }
    \label{fig:sync-cycle}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{exp2/flow.eps}
    \caption[Material flow paths]{Potential material flow paths between facility types.}
    \label{fig:flow}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{ |r | c c | c c | }
        \hline                       
                                          & \multicolumn{2}{c |}{LWR}       & \multicolumn{2}{c |}{SFR} \\
                                          & Cases 1,3 & Cases 2,4 (fleet) & Cases 1,3 & Cases 2,4 (fleet)  \\
        \hline                       
        Cycle length (months)             & 15        & 18                & 12        & 15 \\
        Refueling outage (months)         & 3         & 0                 & 3         & 0 \\
        Batch size ($\text{kg} \cdot \text{HM}$) & 29,565    & 29,565            & 8,025     & 40,125 \\
        Power capacity (MWe)              & 1,080     & 900               & 450       & 360 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \caption[Reactor parameters by case]{
        Reactor configuration for each of the four simulation cases.
    }

    \label{tab:exp2-reactors}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/power.eps}
    \caption[Generated power]{
        Generated power for all four cases.  A fuel shortage occurs from about
        year 100 to about year 140.  In cases 1 and 3 with individual reactor
        modeling, refueling cycles become much more synchronized during and
        after the fuel shortage resuting in large power fluctuations (the
        \emph{cycle staggering effect}).
    }
    \label{fig:exp2-power}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/power-rel.eps}
    \caption[Normalized power]{
        Generated power is normalized to the expected 1\% exponential growth
        curve for all four cases.  A fuel shortage occurs from about year 100
        to about year 140.  The \emph{cycle staggering effect} can be seen as
        divergence from 1.0 and is especially visible in cases 1 and 3 where
        the shortage increases cycle synchronization significantly. The
        \emph{quantized shutdown effect} can also be seen in the discrepency
        between quarterly and monthly time steps for fleet reactor modeling
        (cases 2 and 4) during the shortage; a longer time step causes more
        reactor outage than necessary. The consistent jumping up and down for
        the fleet reactor cases is due to the mis-alignment of reactors going
        offline (multiples of 12 months) and the build period (21 months).
    }
    \label{fig:exp2-power-rel}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/unfueled.eps}
    \caption[Cumulative offline power due to fuel shortage]{
        Cumulative offline power for reactors that had delayed cycle start due
        to fuel shortage. The difference between individual and fleet based
        modeling is primarily a result of the \emph{fuel sharing effect}. The
        difference between monthly and quarterly time steps is primarily
        caused by the \emph{inventory drawdown effect}.
    }
    \label{fig:exp2-unfueled}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/badshare.eps}
    \caption[Cumulative unnecessary idling fuel]{
        Fuel sharing inefficiency approximated by the cumulative number of
        fuel batches given to each reactor on each refueling period multiplied
        by the number of time steps that reactor had to delay the start of its
        next cycle (due to fuel shortage).  Fleet reactors have perfect fuel
        sharing by design and so are not included here. The large difference
        between cases 1 and 3 is mostly due to the \emph{inventory drawdown
        effect}. 
    }
    \label{fig:exp2-badshare}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Pu inventory and flow]{
        Pu inventory and flows for all four cases.  In-flows for cases 1 and 3
        are omitted because they are very noisy and obscure useful other
        information.  Larger time steps results in larger per time step
        material flows. These larger flows mean more material is not available
        for supplying to requesters.  This information lag causes more supply
        constraints than occur with smaller time steps - illustrating the
        \emph{inventory drawdown effect}.
    }
    \label{fig:exp2-puinv}
\end{figure}

>>>>

\documentclass{style}

@@

\usepackage{graphicx}
\usepackage[printwatermark]{xwatermark}
\usepackage{xcolor}
\usepackage{placeins}

@@

There are various low level phenomena that have potential to affect the larger
outcome of simulations with respect to facility modeling decisions.

One difference between the fleet and individual modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short a half batch of fuel it will produce $\frac{5}{6}\cdot C$ of
power for that time step where $C$ is the power capacity of a single reactor
of the fleet (e.g. 1000 MWe).  If an individually modeled reactor is short a
half batch of fuel, then it will produce no power that time step.  Time step
duration can also have this effect.  For both fleet and individual reactor
modeling, power goes offline in for full time steps.  For example, if a
3-batch fleet based reactor is short $\frac{1}{2}$ batch of fuel with a 3
month time step, then it will produce $\frac{5}{6} \cdot 3 \text{mo} \cdot C $
of energy.  In contrast, a monthly time step might allow the same reactor to
produce $[\frac{5}{6} \cdot 1 \text{mo} + 2 \text{mo}] \cdot C $ of energy if
there was actually a fuel shortage for only 1 month.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\columnwidth]{exp2/sync-cycle.eps}
    \caption[The cycle staggering effect]{
        In this scenario, reactors are deployed annualy with a refueling cycle
        length (including outage) of 18 months.  So all reactors deployed
        every 3rd year refuel together.  All initial 100 LWRs start out with
        their cycles synced as well.  While it may look like separate curves,
        this plot shows only a single time series.
    }
    \label{fig:sync-cycle}
\end{figure}

Another difference between fleet-based and individual facility modeling
involves fuel sharing.  Power production by a group of individual reactors for
a fixed amount of fuel shortage may vary depending on how the existing fuel is
distributed.  This is illustrated in Figure \ref{fig:fuel-sharing}.  Being
short 3 batches might mean that one reactor has no batches and isn't operating
or that 3 reactors are missing a single batch.  This will be referred to as
the \emph{fuel sharing effect}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\columnwidth]{exp2/fuel-sharing.pdf}
    \caption[The fuel sharing effect]{
        A simple diagram showing effects of constrained fuel supply
        distribution choices. In both cases A and B, reactor 1 needs 3 new
        fuel batches to operate and reactors 2 and 3 each need 1 fresh batch.
        In case A, the two batches are given to reactors 2 and 3, resulting in
        reactor 1 remaining offline. In case B, the available fuel batches are
        given to reactor 1 resulting in all three reactors being offline.
    }
    \label{fig:fuel-sharing}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.47\textwidth]{exp2/flow.eps}
    \caption[Material flow paths]{Potential material flow paths between facility types.}
    \label{fig:flow}
\end{figure}

@@

@@

\begin{table*}
    \centering
    \begin{tabular}{ |r | c c | c c | }
        \hline                       
                                          & \multicolumn{2}{c |}{LWR}       & \multicolumn{2}{c |}{SFR} \\
                                          & Cases 1,3 & Cases 2,4 (fleet) & Cases 1,3 & Cases 2,4 (fleet)  \\
        \hline                       
        Cycle length (months)             & 15        & 18                & 12        & 15 \\
        Refueling outage (months)         & 3         & 0                 & 3         & 0 \\
        Batch size ($\text{kg} \cdot \text{HM}$) & 29,565    & 29,565            & 8,025     & 40,125 \\
        Power capacity (MWe)              & 1,080     & 900               & 450       & 360 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \caption[Reactor parameters by case]{
        Reactor configuration for each of the four simulation cases.
    }

    \label{tab:exp2-reactors}
\end{table*}

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{exp2/power.eps}
    \caption[Generated power]{
        Generated power for all four cases.  A fuel shortage occurs from about
        year 100 to about year 140.  In cases 1 and 3 with individual reactor
        modeling, refueling cycles become much more synchronized during and
        after the fuel shortage resuting in large power fluctuations (the
        \emph{cycle staggering effect}).
    }
    \label{fig:exp2-power}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{exp2/power-rel.eps}
    \caption[Normalized power]{
        Generated power is normalized to the expected 1\% exponential growth
        curve for all four cases.  A fuel shortage occurs from about year 100
        to about year 140.  The \emph{cycle staggering effect} can be seen as
        divergence from 1.0 and is especially visible in cases 1 and 3 where
        the shortage increases cycle synchronization significantly. The
        \emph{quantized shutdown effect} can also be seen in the discrepency
        between quarterly and monthly time steps for fleet reactor modeling
        (cases 2 and 4) during the shortage; a longer time step causes more
        reactor outage than necessary. The consistent jumping up and down for
        the fleet reactor cases is due to the mis-alignment of reactors going
        offline (multiples of 12 months) and the build period (21 months).
    }
    \label{fig:exp2-power-rel}
\end{figure*}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\columnwidth]{exp2/unfueled.eps}
    \caption[Cumulative offline power due to fuel shortage]{
        Cumulative offline power for reactors that had delayed cycle start due
        to fuel shortage. The difference between individual and fleet based
        modeling is primarily a result of the \emph{fuel sharing effect}. The
        difference between monthly and quarterly time steps is primarily
        caused by the \emph{inventory drawdown effect}.
    }
    \label{fig:exp2-unfueled}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=1.0\columnwidth]{exp2/badshare.eps}
    \caption[Cumulative unnecessary idling fuel]{
        Fuel sharing inefficiency approximated by the cumulative number of
        fuel batches given to each reactor on each refueling period multiplied
        by the number of time steps that reactor had to delay the start of its
        next cycle (due to fuel shortage).  Fleet reactors have perfect fuel
        sharing by design and so are not included here. The large difference
        between cases 1 and 3 is mostly due to the \emph{inventory drawdown
        effect}. 
    }
    \label{fig:exp2-badshare}
\end{figure}

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Pu inventory and flow]{
        Pu inventory and flows for all four cases.  In-flows for cases 1 and 3
        are omitted because they are very noisy and obscure useful other
        information.  Larger time steps results in larger per time step
        material flows. These larger flows mean more material is not available
        for supplying to requesters.  This information lag causes more supply
        constraints than occur with smaller time steps - illustrating the
        \emph{inventory drawdown effect}.
    }
    \label{fig:exp2-puinv}
\end{figure*}
